DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-02-02 paper/overview.tex
..
19 page exact. typo

\begin{figure}[h]
  \centering
%% <<<<<<< HEAD
%%   \includegraphics[width=.5\textwidth]{figs/track_new2}
%%   \caption{One of the custom tracks used for training/testing.}
%%   \label{fig:track}
%% =======
  \begin{subfigure}{0.6\textwidth}
    \includegraphics[width=\textwidth]{figs/track_new2}
    \caption{Track 1.}
    \label{fig:track}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.7\textwidth}
    \includegraphics[width=\textwidth]{figs/track-2}
    \caption{Track 2.}
    \label{fig:track2}
  \end{subfigure}
  \caption{Custom tracks used for training/testing}
  \label{fig:tracks}
%% >>>>>>> f3814396d8701264f2439b42fbe8bbb608c41452
\end{figure}

@@

We would like to stress, however, that the the issues related to the
CNN's accuracies have no impact on the \emph{computational 
aspects of the system}, and that our main focus of this study is
not in improving network accuracy but in closely replicating the
DAVE-2's network architecture and studying its real-time
characteristics.

>>>>

\begin{figure}[h]
  \centering
%% <<<<<<< HEAD
%%   \includegraphics[width=.5\textwidth]{figs/track_new2}
%%   \caption{One of the custom tracks used for training/testing.}
%%   \label{fig:track}
%% =======
  \begin{subfigure}{0.55\textwidth}
    \includegraphics[width=\textwidth]{figs/track_new2}
    \caption{Track 1.}
    \label{fig:track}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.7\textwidth}
    \includegraphics[width=\textwidth]{figs/track-2}
    \caption{Track 2.}
    \label{fig:track2}
  \end{subfigure}
  \caption{Custom tracks used for training/testing}
  \label{fig:tracks}
%% >>>>>>> f3814396d8701264f2439b42fbe8bbb608c41452
\end{figure}

@@

We would like to stress, however, that the issues related to the
CNN's accuracies have no impact on the \emph{computational 
aspects of the system}, and that our main focus of this study is
not in improving network accuracy but in closely replicating the
DAVE-2's network architecture and studying its real-time
characteristics.
